Evaluating infectious disease forecasts with allocation scoring rules

### 2023-07-21 alloscore_manuscript/allocation.tex
add a proposal for a one-paragraph summary of what the allocation score does in intro

>>>>

Briefly, the allocation score of a forecast is the unnecessary realized unmet demand that results from using that forecast to set resource allocations by minimizing expected unmet need --- that is, when we distribute a limited amount $K$ of our resource so that total expected unmet need according to the forecast,
\begin{align}
\sum_i E_{F_i}[\text{unmet need in location $i$}]
\end{align}
is minimized, where the $F_i$ are the marginal forecast distributions for each location. By ``unnecesary'' we mean the unmet need that could have been avoided by an oracle that knows exactly how much need will occur in each location and divides the amount $K$ so that nothing is wasted in one location while it could be put to use in another.
According to the allocation score, one forecast is better than another if it would lead decision-makers to an allocation that results in less unmet need.
